---
title: "NIST Decision Tree Report"
output: pdf_document
params:
  res: NA
  vars_in: NA
  the_proc: NA
  doe_res: NA
  nsd: NA
  doe_type: NA
  diagnostics: NA
  version: NA
  results_table: NA
  the_seed: NA

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Summary
```{r results='asis'}

res = params$res
vars_in = params$vars_in
the_proc = params$the_proc
doe_res = params$doe_res
doe_type = params$doe_type
diagnostics = params$diagnostics
the_seed = params$the_seed

knitr::kable(
  vars_in$the_data
)

cat(paste('Date:', Sys.Date(),'  \n'))
if(doe_type == '1') {
  doe_name = 'Recognizing Dark Uncertainty'
  
} else if(doe_type == '2') {
  doe_name = "Ignoring Dark Uncertainty"
}

cat(paste("Version Number:",version,'  \n'))
cat(paste("Type of DoE: Degrees of Equivalence ",doe_name, '  \n'))
cat(paste("Random Seed:",the_seed,'  \n'))
cat(paste('Selected Procedure:', the_proc,'  \n'))

  # DSL
if(grepl('average',the_proc,TRUE)) {
  
  cat(paste("Consensus estimate:",signif(res$mu,nsd),'  \n'))
  cat(paste("Standard uncertainty:", signif(res$se,nsd),'  \n'))
  cat(paste("Standard uncertainty (using parametric bootstrap):", signif(res$se_dslbs,nsd),'  \n'))
  cat(paste("95% coverage interval: (",signif(res$mu_lower,nsd),", ",signif(res$mu_upper,nsd),")",'  \n',sep=''))
  cat(paste("95% coverage interval (using parametric bootstrap): (",
            signif(res$mu_lower_dslbs,nsd),", ",
            signif(res$mu_upper_dslbs,nsd),")",'  \n',sep=''))
  cat(paste("Dark uncertainty (tau): ",signif(res$tau,nsd),'  \n' ))
  
# weighted median
} else if(grepl('median',the_proc,TRUE)) {

  cat(paste("Consensus estimate:",signif(res$mu,nsd),'  \n'))
  cat(paste("Standard uncertainty:", signif(res$se,nsd),'  \n'))
  cat(paste("95% coverage interval: (",signif(res$mu_lower,nsd),", ",signif(res$mu_upper,nsd),")",'  \n',sep=''))
  
# bayes
} else {

  cat(paste("Consensus estimate:",signif(res$mu,nsd),'  \n'))
  cat(paste("Standard uncertainty:", signif(res$se,nsd),'  \n'))
  cat(paste("95% coverage interval: (",signif(res$mu_lower,nsd),", ",signif(res$mu_upper,nsd),")",'  \n',sep=''))
  cat(paste("Dark uncertainty (tau): ",signif(res$tau,nsd),'  \n' ))
  cat(paste("Tau posterior 0.025 and 0.975 quantiles: ",'(',
            signif(res$tau_lower,nsd),',',signif(res$tau_upper,nsd),')','  \n',sep=''))
}


```

## Decision Tree Hypothesis test results
```{r}
measured_vals = vars_in$measured_vals
standard_unc = vars_in$standard_unc
dof = vars_in$dof

mf_res = metafor::rma(yi = measured_vals,
                   sei = standard_unc,
                   method = "DL")

pval = signif(mf_res$QEp,2)

if(pval < .001) {
  pval = 'p < 0.001'
}

Q_test_dof = length(measured_vals) - 1

# shapiro wilk
mvs = measured_vals
sus = standard_unc
sw_res = stats::shapiro.test((mvs-median(mvs))/sus) 
sym_res = symmetry::symmetry_test(mvs,stat='MGG',bootstrap=TRUE, B=5000) 
```

Cochran's test for Homogeneity:  
```{r results='asis'}
cat(paste("p-value: ",pval,'  \n',
    "Q = ",signif(mf_res$QE,4),' (Reference Distribution: Chi-Square with ',
    Q_test_dof,' Degrees of Freedom)','  \n',
    "tau est. = ",signif(sqrt(mf_res$tau2),4),'  \n',
    "tau/median(x) = ",signif(sqrt(mf_res$tau2)/median(measured_vals),4),'  \n',
    "tau/median(u) = ",signif(sqrt(mf_res$tau2)/median(standard_unc),4),'  \n',sep=''))

```

Shapiro-Wilk test for Normality:
```{r results='asis'}
cat(paste("p =", signif(sw_res$p.value,nsd), '  \n'))
```

Miao-Gel-Gastwirth test of Symmetry:
```{r results='asis'}
cat(paste("p =", signif(sym_res$p.value,nsd)))
```

\newpage

## Plots
```{r, fig.height=4, fig.width=6 }

if(grepl('average',the_proc,TRUE)) {
  kcrv.unc = max(res$se,res$se_dslbs)
} else {
  kcrv.unc = res$se
}

KCplot(val=vars_in$the_data$Result, 
       unc=vars_in$the_data$Uncertainty, 
       tau=res$tau,
       kcrv=res$mu, 
       kcrv.unc=kcrv.unc,
       lab=vars_in$the_data$Laboratory, 
       title=paste("KCRV Estimation:",the_proc), 
       title.position="left",
       ylab=NULL, 
       exclude=vars_in$the_data$Laboratory[!vars_in$which_to_compute])
```

```{r, fig.height=4, fig.width=6 }

doe_data = doe_res$DoE
doe_data[,2:ncol(doe_data)] = signif(doe_data[,2:ncol(doe_data)],nsd)

if(doe_type == "1") {
  doe_data$DoE.Lwr = doe_data$DoE.Lwr.Pred
  doe_data$DoE.Upr = doe_data$DoE.Upr.Pred
  doe_data$DoE.U95 = doe_data$DoE.U95.Pred
  doe_plot_title = 'Unilateral DoE (Recognizing Dark Uncertainty)'
  
} else if(doe_type == "2") {
  doe_data$DoE.Lwr = doe_data$DoE.Lwr.Trade
  doe_data$DoE.Upr = doe_data$DoE.Upr.Trade
  doe_data$DoE.U95 = doe_data$DoE.U95.Trade
  doe_plot_title = 'Unilateral DoE (Ignoring Dark Uncertainty)'
}

outdf = doe_data[,c("Lab","DoE.x","DoE.U95","DoE.Lwr","DoE.Upr")]

DoEplot(outdf,
        doe_plot_title,
        exclude=vars_in$the_data$Laboratory[!vars_in$which_to_compute])
```

\newpage

## DoE Table
```{r}

knitr::kable(
  outdf
)
```

## Lab Uncertainties Table

```{r}

results_table[,2:ncol(results_table)] = signif(results_table[,2:ncol(results_table)],nsd)

knitr::kable(
  results_table[,1:5]
)

knitr::kable(
  results_table[,c(1,6:ncol(results_table))]
)
```


## MCMC Sampler Diagnostics Table (if applicable)

If one of the Bayesian models is run (Hierarchical Gauss-Gauss, Hierarchical Laplace-Gauss, or Hierarchical Skew-Student-t), then diagnostics for the MCMC sampler will be given below. As a general recommendation, if any of the R-hat values are greater than 1.05, then the sampler may not have reached equilibrium, and the “Total Number of MCMC Steps” should be increased, and the run repeated. The “Number of MCMC Warm-Up Steps” should be about half of the “Total Number of MCMC Steps.” The “Effective Sample Size” (n.eff) is approximately the size of the MCMC sample that the results are based on.


```{r}

if(!is.null(diagnostics)) {
  
  diagnostics = as.data.frame(diagnostics)
  
  diagnostics$Rhat = round(diagnostics$Rhat,3)
  
  knitr::kable(diagnostics)
}

```

